The need for accuracy and smoothness in numerical simulations

### 2024-05-14 report/src/draft.tex
Address of GitHub repository updated

\begin{document}
%
\title{The need for accuracy and smoothness in numerical simulations}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Carl Christian Kjelgaard Mikkelsen \inst{1}\orcidID{0000-0002-9158-1941 } \and
  Lori{\'e}n L{\'o}pez-Villellas \inst{2}\orcidID{0000-0002-1891-4359}
  % \and Pablo Garc{\'i}a-Risue{\~no} \inst{3} \orcidID{0000-0002-8142-9196}
}
%
\authorrunning{C. C. Kjelgaard Mikkelsen et al. }
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
  Department of Computing Science, Ume{\aa} University, 90187 Ume{\aa}, Sweden \email{spock@cs.umu.se} \\
  \and Departamento de Inform\'atica e Ingenier\'ia de Sistemas / Arag\'on Institute for Engineering Research (I3A), Universidad de Zaragoza, Zaragoza, Spain \\
  \email{lorien.lopez@unizar.es} \\
 %  \and Independent scholar \\
 %  \email{risueno@unizar.es, garcia.risueno@gmail.com}
}

@@

In this paper we derive and illustrate the use of Richardson extrapolation using a variety of numerical experiments.
GROMACS is a state-of-the-art library for molecular dynamics that is widely used in academia \cite{gromacs2005}.
We demonstrate that the output of the GROMACS is not always amenable to Richardson extrapolation. 
We identify two conditions that are not always satisfied by GROMACS and we demonstrate that each condition is necessary for the successful application of Richardson extrapolation.
Our data and software is freely available from our GitHub \cite{lorien2024ppam} repository along with every script and function needed to replicate every number, table and figure from scratch. The names of our MATLAB functions are written with a typewriter font, e.g., \texttt{plot\_shells}.

>>>>

\begin{document}
%
\title{The need for accuracy and smoothness in numerical simulations}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Carl Christian Kjelgaard Mikkelsen \inst{1}\orcidID{0000-0002-9158-1941 } \and
  Lori{\'e}n L{\'o}pez-Villellas \inst{2}\orcidID{0000-0002-1891-4359}
  % \and Pablo Garc{\'i}a-Risue{\~no} \inst{3} \orcidID{0000-0002-8142-9196}
}
%
\authorrunning{C. C. Kjelgaard Mikkelsen et al. }
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
  Department of Computing Science, Ume{\aa} University, 90187 Ume{\aa}, Sweden \email{spock@cs.umu.se} \\
  \and Barcelona Supercomputing Center, Barcelona, Spain, \\
  \email{lorien.lopez@bsc.es} \\
 %  \and Independent scholar \\
 %  \email{risueno@unizar.es, garcia.risueno@gmail.com}
}

@@

In this paper we derive and illustrate the use of Richardson extrapolation using a variety of numerical experiments.
GROMACS is a state-of-the-art library for molecular dynamics that is widely used in academia \cite{gromacs2005}.
We demonstrate that the output of the GROMACS is not always amenable to Richardson extrapolation. 
We identify two conditions that are not always satisfied by GROMACS and we demonstrate that each condition is necessary for the successful application of Richardson extrapolation.
Our data and software is freely available from our GitHub \cite{spockcc2024ppam} repository along with every script and function needed to replicate every number, table and figure from scratch. The names of our MATLAB functions are written with a typewriter font, e.g., \texttt{plot\_shells}.
